Reference label transfer from the fetal full reference (Cao et al.) for `r params$sample_id`

### 2024-08-28 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
Update 02a_label-transfer_fetal_full_reference_Cao.Rmd

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)
s <- RunAzimuth.Seurat(srat, reference ="fetusref")

>>>>

```{r run_azimuth, message=FALSE, warnings=FALSE}
DefaultAssay(srat) <- "RNA"
options(future.globals.maxSize= 891289600000000)
s <- Azimuth::RunAzimuth(srat, reference ="fetusref")
